A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-03-07 paper/paper.tex
add march meeting talk Tested everything on bingley.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-rods-in-water}
\end{center}
\caption{ Density profiles illustrating the transition from vapor 
to liquid water between the rods. The radius is 0.5~nm, the top figure is 
at a separation of 0.2~nm and the
bottom is 0.6~nm. Figure~\ref{fig:rods-energy-vs-distance} shows
the energy for these and other separations.}
\label{fig:density-rods}
\end{figure}

@@

We extend the study to four rods in water using the same radii as the two rods and
separation distance $d = 0$~nm to $d = 2$~nm for nearest neighbor rods. These exhibit
a similar behavior to the two rods where for small $d$ only vapor is present in the 
middle of the rods until a critical separation between where water occupies the middle.
Before the transition, the four rods and vapor form a square with rounded courners 
where each rod forms a corner (shown in Fig. \ref{fig:density-four-rods} as 'before').
For large $d$, the rods behave like separate single rods.  Free energy
is plotted against rod separation in Fig. \ref{fig:four-rods-energy-vs-distance}.
From the slope we calculate the force per length to be [number].

The rounded square's circumference is estimated by
\begin{equation}
C_{rs} = 2 \pi r + 8r + 4d.
\end{equation}
We again equate this circumference with the total circumference of the four rods, which
results in a critical separation
\begin{equation}
d_{c4} = \frac{3 \pi - 4}{2} r \label{criticalfourrods}
\end{equation}

\begin{table}
\begin{tabular} {|c|c|c|c|}
\hline
$r$ (nm) & $d_{rs}$ prediction (nm) & $d_{c4}$ result (nm) & \% error \\
\hline
0.3 & 0.81 & 0.40 & 51\% \\
\hline
0.5 & 1.36 & 1.15 & 15\% \\
\hline
0.7 & 1.90 & 1.70 & 11\% \\
\hline
0.9 & 2.44 & 2.30 & 06\% \\
\hline
1.0 & 2.70 & 0.00 & 00\% \\
\hline
\end{tabular}
\caption{Calculations of the critical separation (see Equation~\ref{criticalfourrods})
for the transition
from liquid to vapor between four hydrophobic rods.}
\label{criticalfourrodstable}
\end{table}

The predicted and computed valued for $d_{c4}$ are show in Table \ref{criticalfourrodstable}. 
[talk about table here]

@@

Figure~\ref{fig:density-sphere} shows the density profile for several
hard sphere radii, plotted together with with the results of the same
SPC/E molecular dynamics simulation shown in
Figure~\ref{fig:sphere-energy-vs-diameter}\cite{huang2001shs}.  The
agreement with simulation is quite reasonable.  The largest
disagreement involves the density at contact, which according to the
contact value theorem cannot agree, since the free energies do not
agree.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-rods-in-water}
\end{center}
\caption{ Density profiles illustrating the transition from vapor 
to liquid water between the rods. The radius is 0.5~nm, the top figure is 
at a separation of 0.5~nm and the
bottom is 0.6~nm. Figure~\ref{fig:rods-energy-vs-distance} shows
the energy for these and other separations.}
\label{fig:density-rods}
\end{figure}

@@

We simulate four hydrophobic rods in water using the same radii as the two rods and
separation distances $d = 0$~nm to $d = 3$~nm for nearest neighbor rods. We placed
the rods in a 'square' arrangement and observed a similar behavior to the two rods
where vapor is present in between the rods(shown in Fig. \ref{fig:density-four-rods}
as 'before') until a critical separation where it becomes filled with water
(shown in Fig. \ref{fig:density-four-rods} as 'after'). For large $d$,
the rods behave like separate single rods.  Free energy per length
is plotted against rod separation in Fig. \ref{fig:four-rods-energy-vs-distance}.
From the slope we calculate the force per length to be [number].

The rounded square formed by the rods has a circumference estimated by
\begin{equation}
C_{rs} = 2 \pi r + 8r + 4d.
\end{equation}
We again equate this circumference with the total circumference of the four rods, which
results in a critical separation
\begin{equation}
d_{c4} = \frac{3 \pi - 4}{2} r \label{criticalfourrods}
\end{equation}

@@

Figure~\ref{fig:density-sphere} shows the density profile for several
hard sphere radii, plotted together with the results of the same
SPC/E molecular dynamics simulation shown in
Figure~\ref{fig:sphere-energy-vs-diameter}\cite{huang2001shs}.  The
agreement with simulation is quite reasonable.  The largest
disagreement involves the density at contact, which according to the
contact value theorem cannot agree, since the free energies do not
agree.
